### 2019-06-05 dantzig_selector/report/1_introduction.tex
Proof: Finish: Almost-sparsity of
Split chap 3 sources

\Result
{Definition: Restricted Isometry Property}
{
For fixed \m {s =0, \dots N_p -1}, we say that \m {\M{\Phi}} satisfies the restricted isometry property (RIP) of sparsity \m {s} with respect to \m {0 \leq \d_s \leq 1}, if, for all \m {\V {x}}, and for all \m {\MC {A} \subset \MC {T} \SB {N_m}} with \m {\# \MC {A} \leq s},
\Disp {
\NC \NC \RB {1-\d_s} \VNm {\V {x} \DB {\MC {A}}}^2 \NR
\NC \leq \NC \VNm {\M{\Phi} \V {x} \DB {\MC {A}}} _2^2 \NR
\NC \leq \NC \RB {1+\d_s} \VNm {\V {x} \DB {\MC {A}}} _2^2 \NR[+]
}
}
That is, \m {\Phi} is ``almost unitary'' up to ``relative error'' \m {\d_s}.

@@

\Disp{
\NC \NC \RB {\RB {\M{B}^\Tr \otimes \M{A}} \Rm{vec} \SB{\M{X}} } \DB {m_1} \NR
\NC = \NC \sum _{m_2 =0} ^{N_2 N_3 -1} \RB {\M{B}^\Tr \otimes \M{A}} \DB {m_1, m_2} \Rm{vec} \SB {\M{X}} \DB {m_2} \NR
\NC = \NC \sum _{m_2 =0} ^{N_2 N_3 -1} \RB {\M{B}^\Tr} \DB {\Fl{ m_1/N_1 }, \Fl{ m_2/N_2 }}
\M{A} \DB {m_1\; \Rm{Mod}\; N_1, m_2\; \Rm{Mod}\; N_2} \Rm{vec} \SB {\M{X}} \DB {m_2} \NR 
\NC = \NC
\sum _{m_2 =0} ^{N_2 N_3 -1}
\M{B} \DB {\Fl{ m_2/N_2 }, \Fl{ m_1/N_1 }}
\M{A} \DB {m_1\; \Rm{Mod}\; N_1, m_2\; \Rm{Mod}\; N_2} \NR
\NC \NC \Q \Q \Q \Q \Q \Q
\M{X} \DB {m_2\; \Rm{Mod}\; N_2, \Fl{ m_2/N_2 }}
\NR[+]
}

>>>>

\Result
{Definition: Restricted Isometry Property}
{
For fixed \m {s =0, \dots N_p -1}, we say that \m {\M{\Phi}} satisfies the restricted isometry property (RIP) of sparsity \m {s} with respect to \m {0 \leq \d_s \leq 1}, if, for all \m {s}-sparse \m {\V {x}},
\Disp {
\NC \RB {1-\d_s} \VNm {\V {x}}^2
\leq \NC \VNm {\M{\Phi} \V {x}} _2^2 \NR
\NC \leq \NC \RB {1+\d_s} \VNm {\V {x}} _2^2 \NR[+]
}
}
That is, \m {\Phi} is ``almost unitary'' up to ``relative error'' \m {\d_s}.

@@

\Disp{
\NC \NC \RB {\RB {\M{B}^\Tr \otimes \M{A}} \Rm{vec} \SB{\M{X}} } \DB {m_1} \NR
\NC = \NC \sum _{m_2 =0} ^{N_2 N_3 -1} \RB {\M{B}^\Tr \otimes \M{A}} \DB {m_1, m_2} \Rm{vec} \SB {\M{X}} \DB {m_2} \NR
\NC = \NC \sum _{m_2 =0} ^{N_2 N_3 -1} \RB {\M{B}^\Tr} \DB {\Fl{ m_1/N_1 }, \Fl{ m_2/N_2 }}
\M{A} \DB {m_1\; \Rm{Mod}\; N_1, m_2\; \Rm{Mod}\; N_2} \Rm{vec} \SB {\M{X}} \DB {m_2} \NR 
\NC = \NC
\sum _{m_2 =0} ^{N_2 N_3 -1}
\M{B} \DB {\Fl{ m_2/N_2 }, \Fl{ m_1/N_1 }}
\M{A} \DB {m_1\; \Rm{Mod}\; N_1, m_2\; \Rm{Mod}\; N_2} \NR
\NC \NC \SixQ
\M{X} \DB {m_2\; \Rm{Mod}\; N_2, \Fl{ m_2/N_2 }}
\NR[+]
}
